Network Cascades

### 2016-08-25 paper/paper.tex
Introduce the cross section graphs

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.45\textwidth]{img/cascade-regimes.png}
  \caption{Cascade Window}
  \label{fig:cascade-window}
\end{figure}

@@

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.45\textwidth]{img/cascade-regimes-with-cross-section.png}
  \caption{Cascade Window, image from \cite{simplemodel}}
  \label{fig:cascade-window}
\end{figure}

@@

The cascade window diagram is limited to a binary statement wether cascades are possible. To gain further insight on the the nature of cascades inside the window, Watts examined ``cross section'' of the window for $\phi=0.18$ (marked in firgure \ref{fig:cascade-window} with by the densely stroked line at $\phi=0.18$), consisting of serveral measurements. They are depicted in figure \ref{fig:cross-section}. The upper graph (a) maps from $z$ to the amount of steps required for the cascade to occur. The lower figure (b) maps from $z$ to various percentages.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.45\textwidth]{img/cross-section.png}
  \caption{Cross section of the cascade window at $\phi=0.18$, image from \cite{simplemodel}}
  \label{fig:cross-section}
\end{figure}

There are 6 graphs here:

\begin{itemize}
  \item \textbf{Solid Circles \& Solid Line} -- These are optically very hard to distinguish from another, as they are virtually equal. They form the ``upper graph'' in the figure. The former shows the average size of global cascades and the latter shows the (analytical) size of the largest connected component, both as a fraction of the whole network.
  \item \textbf{Open Circles} -- Frequency of global cascades. Forms the ``middle graph''.
  \item \textbf{Short Dashes} -- Fractional (to the size of the network) size of the extended vulnerable cluster. The extended vulnerable cluster comprises the vulnerable cluster plus it's direct neighbors. Forms the ``middle graph''.
  \item \textbf{Long Dashes} -- The fractional (to the size of the network) size of the vulnerable cluster according to an analytical formula derived by Watts in the text. Forms the ``lower graph''.
  \item \textbf{Crosses} -- The fractional (to the size of the network) size of the vulnerable cluster, empirically determined by simulation. Forms the ``lower graph''.
\end{itemize}

Refer to section \ref{sec:findings} for Watts' interpretation of these graphs.
